---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cnvs

<!-- badges: start -->
  [![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
  <!-- badges: end -->

> Canvas LMS API

Minimalistic client to access the
[Canvas LMS API](https://canvas.instructure.com/doc/api/index.html).

Heavily borrowing from the infrastructure of [gh](https://github.com/r-lib/gh) 

## Installation

Install the package from GitHub as usual:

```{r eval = FALSE}
# install.packages("remotes")
remotes::install_github("cwickham/cnvs")
```

### Getting started 

```{r}
library(cnvs)
```

To use the the API to Canvas you need an access token.  Access tokens are specific to your user account and Canvas domain.  Your Canvas domain, `CANVAS_DOMAIN`, is the URL of your institution's Canvas instance, e.g. https://oregonstate.instructure.com or, the instance provided by Instructure https://canvas.instructure.com/.

You can request an access token at: `{CANVAS_DOMAIN}/profile/settings`, under "Approved Integrations:". Once generated, your token is only visible once so make sure you copy it. 

To verify your token and domain, pass them to the `.token()` and `.api_endpoint` arguments of `cnvs_whoami()`:
```{r eval = FALSE}
cnvs_whoami(.token = "mvvGbKyGK9n5T57qhEu8K1sNMt85OLoNGTepqd3v5NEcWMuxArSz5aaXppPjodr5eU",
           .api_url = "https://canvas.instructure.com")
```

The result should be successful and include your name and login id:
```r
  "name": "Charlotte Wickham",
  "login_id": "cwickham@gmail.com",
  "domain": "https://canvas.instructure.com",
  "token": "mv..."
```

It is convenient to set environment variables to store your domain and token.  cnvs looks for these in `CANVAS_DOMAIN` and `CANVAS_API_TOKEN` respectively.  The easiest way to set them is to edit your `.Renviron` file:
```{r, eval = FALSE}
# install.pacakges("usethis")
usethis::edit_r_environ()
```

Add lines like these substituting in your own domain and token:
```
CANVAS_DOMAIN="https://canvas.instructure.com"
CANVAS_API_TOKEN="mvvGbKyGK9n5T57qhEu8K1sNMt85OLoNGTepqd3v5NEcWMuxArSz5aaXppPjodr5eU"

```

Restart R and check by running `cnvs_whoami()` with no arguments:
```{r, eval = FALSE}
cnvs_whoami()
```

```r
  "name": "Charlotte Wickham",
  "login_id": "cwickham@gmail.com",
  "domain": "https://canvas.instructure.com",
  "token": "mv..."
```

## Usage

Use the `cnvs()` function to access all API endpoints. The endpoints are
listed in the [documentation](https://canvas.instructure.com/doc/api/index.html).

The first argument of `cnvs()` is the endpoint. Note that the leading `/api/v1/` must be included as well, but this facilitates copy and pasting directly from the documentation. Parameters can be passed as extra arguments. E.g.

```{r}
my_courses <- cnvs("/api/v1/courses", enrollment_type = "teacher")
vapply(my_courses, "[[", "", "name")
```

The JSON result sent by the API is converted to an R object.

If the end point itself has parameters, these can also be passed
as extra arguments:

```{r}
test_modules <- cnvs("/api/v1/courses/:course_id/modules", 
  course_id = 1732420)
vapply(test_modules, "[[", "", "name")
```


### POST, PATCH, PUT and DELETE requests

POST, PUT, and DELETE requests can be sent by including the
HTTP verb before the endpoint, in the first argument. For example, to
create a module:
```{r}
new_module <- cnvs("POST /api/v1/courses/:course_id/modules",
  course_id = 1732420,  # set a parameter in the endpoint `:course_id`
  module = list(        # a parameter sent in the body
    name = "First module",
    position = 1
  )
)
```

```{r}
test_modules <- cnvs("/api/v1/courses/:course_id/modules", 
  course_id = 1732420)
vapply(test_modules, "[[", "", "name")
```

Then update the name of the module:
```{r}
update_module <- cnvs("PUT /api/v1/courses/:course_id/modules/:id",
  course_id = 1732420,
  id = new_module$id,
  module = list(
    name = "Module 1"
  )
)
```

```{r}
test_modules <- cnvs("/api/v1/courses/:course_id/modules", 
  course_id = 1732420)
vapply(test_modules, "[[", "", "name")
```

Then, finally, delete the module:
```{r}
cnvs("DELETE /api/v1/courses/:course_id/modules/:id",
  course_id = 1732420,
  id = new_module$id
)
```

```{r}
test_modules <- cnvs("/api/v1/courses/:course_id/modules", 
  course_id = 1732420)
vapply(test_modules, "[[", "", "name")
```

### Pagination

Supply the `page` parameter to get subsequent pages:

```{r eval = FALSE}
my_courses2 <- cnvs("/api/v1/courses", enrollment_type = "teacher",
  page = 2)
vapply(my_courses2, "[[", "", "name")
```

## License

cnvs: MIT © Charlotte Wickham

The code is mostly minor edits to the [gh](https://github.com/r-lib/gh) package:

gh: MIT © Gábor Csárdi, Jennifer Bryan, Hadley Wickham
