---
format: gfm
execute:
  collapse: true
  comment: "#>"
knitr:
  opts_chunk:
    fig.path: "man/figures/README-"
    out.width: "100%"
---

<!-- README.md is generated from README.qmd. Please edit that file -->

# cnvs

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

Minimalistic client to access the
[Canvas LMS API](https://canvas.instructure.com/doc/api/index.html).  Heavily borrowing from the infrastructure of [gh](https://github.com/r-lib/gh)

## Philosophy

cnvs is intentionally minimalist.  To use it, you will need to become familiar with the [Canvas API documentation](https://canvas.instructure.com/doc/api/index.html).  cnvs does no checking on the endpoints you provide, nor the objects you pass.  This has the advantage that cnvs is not dependent on the specifics of the Canvas API.  cnvs also does no parsing of response content, you will need to extract the desired information from the returned lists yourself.

While cnvs does facilitate the automation of repetitive tasks in Canvas from R,  it still requires a fair bit of expertise from the user.  The hope is to use it as a foundation for a higher level api package, that is more user-friendly.

## Installation

Install the package from GitHub:

```{r}
#| label: install
#| eval: false
# install.packages("remotes")
remotes::install_github("cwickham/cnvs")
```

## Usage

```{r}
#| label: setup
library(cnvs)
```

Use the `cnvs()` function to access all API endpoints. The endpoints are
listed in the [documentation](https://canvas.instructure.com/doc/api/index.html).

The first argument of `cnvs()` is the endpoint. Note that the leading `/api/v1/` must be included as well, but this facilitates copy and pasting directly from the documentation. Parameters can be passed as extra arguments. E.g.

```{r}
#| label: list-courses
my_courses <- cnvs("/api/v1/courses", enrollment_type = "teacher")
vapply(my_courses, "[[", "", "name")
```

The JSON result sent by the API is converted to an R object.

If the end point itself has parameters, these can also be passed
as extra arguments:

```{r}
#| label: list-modules
test_modules <- cnvs("/api/v1/courses/:course_id/modules",
  course_id = 14337283)
vapply(test_modules, "[[", "", "name")
```


### POST, PATCH, PUT and DELETE requests

POST, PUT, and DELETE requests can be sent by including the
HTTP verb before the endpoint, in the first argument. For example, to
create a module:

```{r}
#| label: create-module
new_module <- cnvs("POST /api/v1/courses/:course_id/modules",
  course_id = 14337283,  # set a parameter in the endpoint `:course_id`
  module = list(        # a parameter sent in the body
    name = "First module",
    position = 1
  )
)
```

```{r}
#| label: list-modules-after-create
test_modules <- cnvs("/api/v1/courses/:course_id/modules",
  course_id = 14337283)
vapply(test_modules, "[[", "", "name")
```

Then update the name of the module:

```{r}
#| label: update-module
update_module <- cnvs("PUT /api/v1/courses/:course_id/modules/:id",
  course_id = 14337283,
  id = new_module$id,
  module = list(
    name = "Module 1"
  )
)
```

```{r}
#| label: list-modules-after-update
test_modules <- cnvs("/api/v1/courses/:course_id/modules",
  course_id = 14337283)
vapply(test_modules, "[[", "", "name")
```

Then, finally, delete the module:

```{r}
#| label: delete-module
cnvs("DELETE /api/v1/courses/:course_id/modules/:id",
  course_id = 14337283,
  id = new_module$id
)
```

```{r}
#| label: list-modules-after-delete
test_modules <- cnvs("/api/v1/courses/:course_id/modules",
  course_id = 14337283)
vapply(test_modules, "[[", "", "name")
```

### Pagination

Supply the `page` parameter to get subsequent pages:

```{r}
#| label: pagination
#| eval: false
my_courses2 <- cnvs("/api/v1/courses", enrollment_type = "teacher",
  page = 2)
vapply(my_courses2, "[[", "", "name")
```

## License

cnvs: MIT © Charlotte Wickham

The code is mostly minor edits to the [gh](https://github.com/r-lib/gh) package:

gh: MIT © Gábor Csárdi, Jennifer Bryan, Hadley Wickham
