---
title: "Getting started with cnvs"
vignette: >
  %\VignetteIndexEntry{Getting started with cnvs}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
execute:
  eval: false
  collapse: true
  comment: "#>"
---

```{r}
#| label: setup
library(cnvs)
library(purrr)
library(dplyr)
```

```{r}
#| label: setup-test-resources
#| include: false
account_id <- 81259

# Create a new course for testing (enroll_me adds creator as teacher)
test_course <- cnvs(
  "POST /api/v1/accounts/:account_id/courses",
  account_id = account_id,
  course = list(
    name = "cnvs test course",
    course_code = "CNVS101"
  ),
  enroll_me = TRUE
)$id

# Create discussions for examples
discussion1 <- cnvs(
  "POST /api/v1/courses/:course_id/discussion_topics",
  course_id = test_course,
  title = "Welcome to the course",
  message = "Introduce yourself here!"
)

discussion2 <- cnvs(
  "POST /api/v1/courses/:course_id/discussion_topics",
  course_id = test_course,
  title = "Questions about Assignment 1",
  message = "Post your questions here."
)

# Create an announcement
announcement <- cnvs(
  "POST /api/v1/courses/:course_id/discussion_topics",
  course_id = test_course,
  title = "Course starts Monday!",
  message = "Looking forward to seeing you all.",
  is_announcement = TRUE
)
```

## Credentials

To use the API to Canvas you need an access token. Access tokens are specific to your user account and Canvas domain. Your Canvas domain, `CANVAS_DOMAIN`, is the URL of your institution's Canvas instance, e.g. <https://oregonstate.instructure.com> or the instance provided by Instructure <https://canvas.instructure.com/>.

You can request an access token at: `{CANVAS_DOMAIN}/profile/settings`, under "Approved Integrations:". Once generated, your token is only visible once so make sure you copy it.

To verify your token and domain, pass them to the `.token` and `.api_url` arguments of `cnvs_whoami()`:

```{r}
#| label: whoami-explicit
#| eval: false
cnvs_whoami(
  .token = "your-token-here",
  .api_url = "https://canvas.instructure.com"
)
```

The result should be successful and include your name and login id:

```
  "name": "Charlotte Wickham",
  "login_id": "cwickham@gmail.com",
  "domain": "https://canvas.instructure.com",
  "token": "yo..."
```

It is convenient to set environment variables to store your domain and token. cnvs looks for these in `CANVAS_DOMAIN` and `CANVAS_API_TOKEN` respectively. The easiest way to set them is to edit your `.Renviron` file:

```{r}
#| label: edit-renviron
#| eval: false
# install.packages("usethis")
usethis::edit_r_environ()
```

Add lines like these substituting in your own domain and token:

```
CANVAS_DOMAIN="https://canvas.instructure.com"
CANVAS_API_TOKEN="your-token-here"

```

Make sure your `.Renviron` file ends with an empty line.

Restart R and check by running `cnvs_whoami()` with no arguments:

```{r}
#| label: whoami
cnvs_whoami()
```

```default
{
  "name": "Charlotte Wickham",
  "login_id": "116595056272912288897",
  "domain": "https://canvas.instructure.com",
  "token": "7~JU...mQac"
}
```

## Finding your courses

The default `cnvs()` endpoint is `/api/v1/courses` which lists all your courses:

```{r}
#| label: list-courses
cnvs()
```

It's easier to work with this data if you extract the course names and IDs into a tibble:

```{r}
#| label: courses-tibble
cnvs() |> map(\(x) tibble(id = x$id, name = x$name)) |> list_rbind()
```


You can also find your course ID by visiting your course in Canvas and examining the URL:

```
https://canvas.instructure.com/courses/1732420
```

Your course ID comes right after `/courses/`, e.g. 1732420 in this case.

For the examples below, I'll use a `course_id` from one of my courses --- you'll need to substitute your own:

```{r}
#| label: set-course-id
#| eval: false
course_id <- 14337283
```

```{r}
#| label: set-course-id-real
#| include: false
course_id <- test_course
```

## Making queries

To make a query to the Canvas LMS API use the `cnvs()` function. The first argument is the API endpoint. `cnvs()` is designed to make it as easy as possible to copy and paste from the [Canvas API documentation](https://canvas.instructure.com/doc/api/) (also available at [developerdocs.instructure.com](https://developerdocs.instructure.com/services/canvas)).

As an example, imagine you want to see the discussion topics in your course. Your first step is to find this task in the Canvas API docs --- it is listed under the Discussions resource as [List discussion topics](https://canvas.instructure.com/doc/api/discussion_topics.html#method.discussion_topics.index). There are two endpoints listed there:

> GET /api/v1/courses/:course_id/discussion_topics

> GET /api/v1/groups/:group_id/discussion_topics

The first will list topics in a course and the second in a group --- you want the first. Parts of the endpoint that are prefaced with a colon, `:`, are parameters, e.g. `:course_id` and `:group_id`. You will need to provide these parameters to `cnvs()` as named arguments (minus the `:`).

To make the query, copy and paste the endpoint to the first argument of `cnvs()`, then add arguments for any parameters in the endpoint:

```{r}
#| label: get-discussions
discussions <- cnvs(
  "GET /api/v1/courses/:course_id/discussion_topics",
  course_id = course_id
)
```

## Parsing responses

`cnvs()` returns a list, but prints this list as JSON. You can access components as you would elements in a list:

```{r}
#| label: access-element
discussions[[1]]$title
```

Functions for parsing the results are beyond the scope of cnvs, but you can parse them yourself using iteration functions from purrr. For example, we could look at all the topic titles:

```{r}
#| label: map-titles
discussions |>
  map_chr("title")
```

Or squeeze the entire response into a tibble:

```{r}
#| label: discussions-tibble
discussions |>
  map(\(x) {
    x |>
      compact() |> # remove NULLs
      map_if(is.list, list) |> # push nested lists down one level
      as_tibble()
  }) |>
  list_rbind()
```

## Passing parameters to the endpoint

The Canvas API docs also describe parameters that can be passed in the body of a query to each endpoint in the "Parameters" section. You can add these as additional named arguments to `cnvs()`. For example, for [List discussion topics](https://canvas.instructure.com/doc/api/discussion_topics.html#method.discussion_topics.index) a possible parameter is `only_announcements`, a boolean, that controls whether only announcements are returned. You could add this to the call the `cnvs()` as another argument:

```{r}
#| label: get-announcements
announcements <- cnvs(
  "GET /api/v1/courses/:course_id/discussion_topics",
  course_id = course_id,
  only_announcements = TRUE
)
announcements |>
  map_chr("title")
```

Some parameters expect a more complicated object, for example the parameters to [create a module](https://canvas.instructure.com/doc/api/modules.html#method.context_modules_api.create), include:

> `module[name]`
> `module[unlock_at]`
> `module[position]`

This notation, a parameter name followed by another in square brackets, indicates a hierarchical structure. Canvas is expecting the `module` parameter to be a JSON object. In `cnvs()` this translates to a named list, e.g.:

```{r}
#| label: create-module
new_module <- cnvs(
  "POST /api/v1/courses/:course_id/modules",
  course_id = course_id,
  module = list(
    name = "First module",
    unlock_at = "2019-09-01T6:59:00Z",
    position = 1
  )
)
```

If the square brackets are empty, Canvas is expecting a JSON array, which translates to an unnamed list in `cnvs()`. An example of this structure is the `quiz_extensions` parameter to [set quiz extensions](https://canvas.instructure.com/doc/api/quiz_extensions.html#method.quizzes/quiz_extensions.create), e.g.

> `quiz_extensions[][user_id]`
> `quiz_extensions[][extra_attempts]`

```{r}
#| label: quiz-extensions
#| eval: false
quiz_ext <- cnvs(
  "POST /api/v1/courses/:course_id/quizzes/:quiz_id/extensions",
  course_id = course_id,
  quiz_id = 62851823,
  quiz_extensions = list(
    list(
      user_id = 99999,
      extra_attempts = 1
    ),
    list(
      user_id = 99998,
      extra_attempts = 2
    )
  )
)
```

## Uploading files

To upload files use the `cnvs_upload()` function. You need to locate the endpoint for the required context of the file. E.g. To [upload a course file](https://canvas.instructure.com/doc/api/courses.html#method.courses.create_file) the endpoint is:

```
POST /api/v1/courses/:course_id/files
```

Whereas to [upload a file as a submission](https://canvas.instructure.com/doc/api/submissions.html#method.submissions_api.create_file) the endpoint is:

```
POST /api/v1/courses/:course_id/assignments/:assignment_id/submissions/:user_id/files
```

Pass the path to the file you wish to upload to `cnvs_upload()`:

```{r}
#| label: create-temp-file
#| include: false
temp_file <- tempfile("cnvs-example-", fileext = ".txt")
writeLines("This is an example file for the cnvs vignette.", temp_file)
```

```{r}
#| label: upload-file
uploaded <- cnvs_upload(
  temp_file,
  course_id = course_id,
  parent_folder_path = "handouts/"
)
```

The default endpoint uploads to a course. Like `cnvs()` you can specify endpoint parameters like `course_id`, or request body parameters like `parent_folder_path`, as additional arguments.

```{r}
#| label: cleanup
#| include: false

# Delete the test course (this deletes all content within it too)
cnvs(
  "DELETE /api/v1/courses/:course_id",
  course_id = test_course,
  event = "delete"
)

# Clean up temp file
unlink(temp_file)
```
